### 2025-02-21 paper-reviews/papers-2025.tex
Add DeepSeek-V3 paper

\section*{Machine Learning}
\begin{itemize}
    \item \cite{Behrouz:Titans:2024}:

>>>>

\section*{Machine Learning}
\begin{itemize}
    \item \cite{DeepSeekAI:2025:DeepSeekV3}:

    The report presents DeepSeek-V3 model architecture. The key difference from the Transformer architecture are: using Multi-Head Latent Attention (MLA) instead of MHA; using Mixture of Experts (MoE) instead of Feed Forward Network. DeepSeek-V3 MoE consists of shared and routed experts. Every token will run through the shared experts and select a few routed once. Each token may potentially end up using completely different routed experts. MLA implementation is aimed to reduce KV-cache usage by having a single shared cache for all heads. It may sound similar to Grouped Query Attention (GQA) but instead of compressing information from multiple heads into one, MLA moves per-head key and value information to per-head query thus only having the common for all heads information in keys and values. The authors also introduce Multi-Token Prediction (MTP) module that is used for training in the original work but can potentially be used for speculatively predicting several tokens in one run of the model.

    \item \cite{Behrouz:Titans:2024}:
